\documentclass{article}

\usepackage{tabularx}
\usepackage{booktabs}

\title{SE 3XA3: Problem Statement\\Spann}

\author{Team 8
		\\ Christopher Stokes | stokescd
		\\ Varun Hooda | hoodav
}

\date{}

\input{../Comments}

\begin{document}

\begin{table}[hp]
\caption{Revision History} \label{TblRevisionHistory}
\begin{tabularx}{\textwidth}{llX}
\toprule
\textbf{Date} & \textbf{Developer(s)} & \textbf{Change}\\
\midrule
    Sept. 22, 2016 & Christopher, Varun & Initial problem statement\\
\bottomrule
\end{tabularx}
\end{table}

\newpage

\maketitle

\large
\textbf{“Why is this an important problem?}\\
\normalsize

Development is often a challenging process that has many points of failure.
This is why developers often make use of tools and software applications that
make the entire process easier to manage and maintain, as well as reduce the
overall effort and time that has to be put in by developers. Web-based
coding/development solutions, such as the one we are basing our project on,
often lack many features and functionality that make modern software
development more efficient. Thus the benefits of such online platforms are
often outweighed by their lack of features and functionality. Solving this
issue will provide developers with the benefits of an online, web-based,
development platform while retaining the benefits of traditional desktop IDEs.
Thus, increasing the efficiency of the entire software development processes.\\

\large
\textbf{What problem are you trying to solve?}\\
\normalsize

The project Spann is attempting to solve the issue with delays in development
caused by compiler and interpreter setup and maintenance,  IDE maintenance,
files system maintenance and dependency control. This problem is especially
noticeable on smaller projects where the delay in development is a much higher
percentage of the overall time. The project therefore focuses on providing a
quick and easy system for the user, with features specific to making
development fast. This means lowering the time impact of the multitude of
issues that slow down development. or impede actual development tasks. This
includes language and compiler install time, renaming and refactoring, simple
syntax mistakes and incorrect names.\\

\large
\textbf{What is the context of the problem you are solving?}\\
\normalsize

The primary stakeholders of Spann are developers who need to prototype or test
sections of code, and developers working on the project when they do not want
to have to manage the language dependencies themselves. By having the platform
run independently of a user’s system, we’re able to make Spann accessible to
more people by removing the complexity, effort and time of setting up a
development environment. This makes it ideal for developers working on
different platforms and devices that may not support the language or have
complications with setting up the environment. It also is ideal for developers
working on subsections of a larger project, giving them the ability to quickly
implement algorithms with fewer faults away from the complications of the
larger project.\\

\wss{comment}

\ds{comment}

\mj{comment}

\cm{comment}

\mh{comment}

\end{document}
